%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer}
    {OmiseGO}
    {Bangkok, Thailand}
    {Nov, 2017 - Dec, 2020}
    {
      \begin{cvitems}
        \item {Developed A sample android application for demonstrating eWallet functionalities \textbf{https://github.com/omisego/sample-android}}
        \item {Developed 2FA authentication for the eWallet and adding small features \textbf{https://github.com/omisego/ewallet}}
        \item {Developed merchant and customer android application to demonstrate scenario for the real-world usage \textbf{https://github.com/omisego/pos-client-android} and \textbf{https://github.com/omisego/pos-merchant-android}}
        \item {Developed an Ethereum layer-2 wallet application with React Native.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Ascend Corp.} % Organization
    {Bangkok, Thailand} % Location
    {Oct, 2016 - Oct, 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed RESTful API server with automated tests for merchant registration TrueMoney system.}
        \item {Developed an android application, TrueMoney Wallet, one of the leading financial services application in Thailand.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Android Developer} % Job title
    {Socket 9 Co., Ltd.} % Organization
    {Bangkok, Thailand} % Location
    {July. 2015 - Sep. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed android application TSL auto corporation. \textbf{Download https://goo.gl/M9LGYQ}}
        \item {Developed android application NaviGo Thailand. Car transportation app. \textbf{Download https://goo.gl/31FqZz}}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
